Modelling Weddell Sea Food Web

### 2022-02-09 ModellingWeddellSea.Rmd
Calculate unweighted topological metrics

@@

```{r readWeddell, eval=F,echo=F,message=T,warning=T}

#
# Read and check data available on GATEWAy about Weddell Sea
#
source("R/network_fun.r")
require(igraph)
require(multiweb)
require(tidyverse)

# Read the original database
#
ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv",col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
names(ga)
wedd_df <-  ga %>%filter(grepl('Weddell',foodweb.name))  #saveRDS(wedd_df, "Data/wedd_df.rds")

@@

```{r makeBodyMass, eval=F,echo=F,message=T,warning=T}

@@

save.image()

@@

@@

>>>>

## Setup

```{r setup, eval=TRUE,echo=F,message=T,warning=T}

if(file.exists(".RData")) load(".RData")

source("R/network_fun.r")
require(igraph)
require(multiweb)
require(tidyverse)

@@

```{r readWeddell, eval=FALSE,echo=F,message=T,warning=T}

#
# Read and check data available on GATEWAy about Weddell Sea
#
# Read the original database
#
ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv",col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
names(ga)
wedd_df <-  ga %>%filter(grepl('Weddell',foodweb.name))  #saveRDS(wedd_df, "Data/wedd_df.rds")

@@

```{r makeBodyMass, eval=FALSE,echo=F,message=T,warning=T}

@@

@@

rm(detritus,wedd,wedd_df1)
save.image()

@@

## Calc unweighted topological indices

```{r calcunweightedtopo, eval=TRUE,echo=F,message=T,warning=T}

websTbl <- tibble()
curveBallNets <- tibble()

tp <- calcTopologicalIndices(g)
#tp <- bind_cols(tp, calcIncoherence(g1)) 
tp <- bind_cols(tp, calc_QSS(g,10000,48, istrength=FALSE))

websTbl <- bind_rows(websTbl, tp)

lred <- curveBall(g,1000)
tp <- calcTopologicalIndices(lred,ncores=48)

tp0 <- calcModularitySWnessZScore(g,lred,ncores=48)
tp1 <- tp0$da %>% dplyr::select(Modularity:isSWness)
websTbl <- bind_cols(websTbl,tp1)

curveBallNets <- tp0$sims 
rm(tp,tp0,lred,tp1)
save.image()
